Systematic studies of correlations between different order flow harmonics in $\PbPb$ collisions at $\snn = 2.76$~TeV

### 2017-07-19 appendix.tex

% !TEX root = paper.tex
\appendix
\section{Model comparisons of the Individual flow harmonics $v_n$}
\label{sec:vn}
As discussed in Sec.~\ref{sec:method}, NSC$(m,n)$ is expected to be insensitive to the magnitudes of $v_{m}$ and $v_{n}$ but SC$(m,n)$ has contributions from both the correlations between the two different flow harmonics and the individual harmonics $v_{n}$. Therefore it is important to check how well the theoretical models used in Sec.~\ref{sec:theory} describe the measured $v_n$ data shown in Sec.~\ref{sec:results}. The comparisons are made only up to $v_4$ because model calculations are not available for $v_5$ at this moment.

@@

The VISH2+1 calculations with various initial conditions and $\eta/s$ parameters are compared to the $v_n$ data in Fig.~\ref{fig:Figure_A2}.
Neither MC-Glauber nor MC-KLN initial conditions can simultaneously describe $v_2$, $v_3$ and $v_4$. In particular, for MC-Glauber initial conditions, VISH2+1 with $\eta/s$ = 0.08 can nicely describe $v_2$ from central to midcentral collisions, but overestimates $v_3$ and $v_4$ for the same centrality ranges. For MC-KLN initial conditions, VISH2+1 with $\eta/s$ = 0.20 reproduces $v_2$ but underestimates $v_3$ and $v_4$ for the presented centrality regions. The calculations with AMPT initial conditions improves the simultaneous descriptions of $v_n$ ($n$ = 2, 3 and 4). The overall difference to the data is quite large if all the model settings are considered, about 30\% for $v_n$ ($n$ = 2 and 3) and 50\% for $v_4$. The calculations with AMPT initial conditions reproduce the observed centrality dependence with an accuracy of 10-20\%.

>>>>

% !TEX root = paper.tex
\appendix
\section{Model Comparisons of the Individual Flow Harmonics $v_n$}
\label{sec:vn}
As discussed in Sec.~\ref{sec:method}, NSC$(m,n)$ is expected to be insensitive to the magnitudes of $v_{m}$ and $v_{n}$ but SC$(m,n)$ has contributions from both the correlations between the two different flow harmonics and the individual harmonics $v_{n}$. Therefore it is important to check how well the theoretical models used in Sec.~\ref{sec:theory} describe the measured $v_n$ data shown in Sec.~\ref{sec:results}. The comparisons are made only up to $v_4$ because model calculations are not available for $v_5$ at this moment.

@@

The VISH2+1 calculations with various initial conditions and $\eta/s$ parameters are compared to the $v_n$ data in Fig.~\ref{fig:Figure_A2}.
Neither MC-Glauber nor MC-KLN initial conditions can simultaneously describe $v_2$, $v_3$ and $v_4$. In particular, for MC-Glauber initial conditions, VISH2+1 with $\eta/s$ = 0.08 can describe well $v_2$ from central to midcentral collisions, but overestimates $v_3$ and $v_4$ for the same centrality ranges. For MC-KLN initial conditions, VISH2+1 with $\eta/s$ = 0.20 reproduces $v_2$ but underestimates $v_3$ and $v_4$ for the presented centrality regions. The calculations with AMPT initial conditions improves the simultaneous descriptions of $v_n$ ($n$ = 2, 3 and 4). The overall difference to the data is quite large if all the model settings are considered, about 30\% for $v_n$ ($n$ = 2 and 3) and 50\% for $v_4$. The calculations with AMPT initial conditions reproduce the observed centrality dependence with an accuracy of 10-20\%.

### 2017-07-19 longSC.tex

As discussed in Sec.~\ref{sec:method}, the NSC($m$,$n$) observables are normalized by the product $\left<v_{m}^2\right>\left<v_{n}^2\right>$.
These products are obtained from two-particle correlations using a pseudorapidity gap of $|\Delta\eta| > 1.0$. We use the notation $v_n$ instead of $v_{n}\{2, |\Delta\eta|>1\}$ used in \cite{Adam:2016izf} and they are $p_{\rm T}$ integrated.
%While these product are reconstructed and normalized directly for NSC calculations,
The complete sets of the individual flow harmonics $v_n$ used to calculate the NSC observables are shown in Fig.~\ref{fig:Figure_2A}.
The centrality dependence of $v_n$ ($n$ = 2, 3, 4 and 5) is shown in the left panels ((A), (B) and (C)) of  Fig.~\ref{fig:Figure_2A}. The $v_n$ values ($n < 5$) are equivalent to those in \cite{Adam:2016izf}. The $5^{\mathrm{th}}$ order flow harmonic $v_5$ is shown in panel (C). The $p_{\rm T, min}$ dependence of $v_n$ ($n$ = 2, 3 and 4) is shown in the right panels ((a), (b) and (c)) of Fig.~\ref{fig:Figure_2A} in all centrality ranges relevant to the measured NSC($m$,$n$) observables.

@@

The comparison to the VISH2+1 calculation~\cite{Zhu:2016puf} is shown in Fig.~\ref{fig:Figure_4}.  All calculations with large $\eta/s$ regardless of the initial conditions ($\eta/s=0.2$ for MC-KLN and MC-Glauber initial conditions and $\eta/s=0.16$ for AMPT initial conditions) fail to capture the centrality dependence of the SC($m$,$n$) observables of all orders, shown in the left panels in Fig.~\ref{fig:Figure_4}.
Among the calculations with small $\eta/s$ ($\eta/s=0.08$), the one with the AMPT initial conditions describes the data better than the ones with other initial conditions for all SC($m$,$n$) observables measured, but it cannot describe the data quantitively for most of the centrality ranges.
Similar to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}, the sign of the normalized NSC(3,2) in the model calculations in Fig.~\ref{fig:Figure_4} is opposite to that in data in 5--10\% central collisions. 
NSC(3,2) and NSC(4,3) are not very sensitive to the initial conditions or $\eta/s$ parameterization used in the model, and are not described quantitatively.

>>>>

As discussed in Sec.~\ref{sec:method}, the NSC($m$,$n$) observables are normalized by the product $\left<v_{m}^2\right>\left<v_{n}^2\right>$.
These products are obtained from two-particle correlations using a pseudorapidity gap of $|\Delta\eta| > 1.0$. 
In this paper we shortly denote the $p_{\rm T}$ integrated $v_{n}\{2, |\Delta\eta|>1\}$ as $v_n$.
%We use the notation $v_n$ instead of $v_{n}\{2, |\Delta\eta|>1\}$ used in \cite{Adam:2016izf} and they are $p_{\rm T}$ integrated.
%While these product are reconstructed and normalized directly for NSC calculations,
The complete sets of the individual flow harmonics $v_n$ used to calculate the NSC observables are shown in Fig.~\ref{fig:Figure_2A}.
The centrality dependence of $v_n$ ($n$ = 2, 3, 4 and 5) is shown in the left panels ((A), (B) and (C)) of  Fig.~\ref{fig:Figure_2A}. The $v_n$ values ($n < 5$) are equivalent to those in \cite{Adam:2016izf}. The $5^{\mathrm{th}}$ order flow harmonic $v_5$ is shown in panel (C). The $p_{\rm T, min}$ dependence of $v_n$ ($n$ = 2, 3 and 4) is shown in the right panels ((a), (b) and (c)) of Fig.~\ref{fig:Figure_2A} in all centrality ranges relevant to the measured NSC($m$,$n$) observables.

@@

The comparison to the VISH2+1 calculation~\cite{Zhu:2016puf} is shown in Fig.~\ref{fig:Figure_4}.  All calculations with large $\eta/s$ regardless of the initial conditions ($\eta/s=0.2$ for MC-KLN and MC-Glauber initial conditions and $\eta/s=0.16$ for AMPT initial conditions) fail to capture the centrality dependence of the SC($m$,$n$) observables of all orders, shown in the left panels in Fig.~\ref{fig:Figure_4}.
Among the calculations with small $\eta/s$ ($\eta/s=0.08$), the one with the AMPT initial conditions describes the data better than the ones with other initial conditions for all SC($m$,$n$) observables measured, but it cannot describe the data quantitively for most of the centrality ranges.
Similar to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}, the sign of the normalized NSC(3,2) in the model calculations in Fig.~\ref{fig:Figure_4} is opposite to that in data in 5--10\% central collisions. 
%NSC(3,2) and NSC(4,3) are not very sensitive to the initial conditions or $\eta/s$ parameterization used in the model, and are not described quantitatively.
The comparisons of the measured NSC(3,2) and NSC(4,3) to VISH2+1 model calculations suggest that they are not very sensitive to the initial conditions or $\eta/s$ parameterization, though the model does not describe them quantitatively.
